### 2022-12-14 code/2_combine/2_combine.Rmd
setting up cogsci paper

```{r loading data E, warning=FALSE, include=F}
df.resp_E <- read.csv("../../data/dataUS_excl.csv") %>%
  select(-X)
```

```{r loading data V, include=F}
df.resp_V <- read.csv("../../data/dataVN_excl.csv") %>%
  select(-X)
```

```{r loading data M, warning=FALSE, include=F}
df.resp_M <- read.csv("../../data/dataCN_excl.csv") %>%
  select(-X)
```

>>>>

```{r loading data E, warning=FALSE, include=F}
df.resp_E <- read.csv("../../data/responding/dataUS_excl.csv") %>%
  select(-X)
```

```{r loading data V, include=F}
df.resp_V <- read.csv("../../data/responding/dataVN_excl.csv") %>%
  select(-X)
```

```{r loading data M, warning=FALSE, include=F}
df.resp_M <- read.csv("../../data/responding/dataCN_excl.csv") %>%
  select(-X)
```

### 2022-12-14 code/3_analysis/3_analysis_compare_freq_cosine.Rmd
setting up cogsci paper

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
library("Hmisc")
library("dplyr")

@@

fit.EN_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(near(theme_match_frequency_E, .Machine$double.eps) & 
                                  near(tax_match_frequency_E, .Machine$double.eps))),

@@

>>>>

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
#library("Hmisc")
library("dplyr")

@@

fit.EN_US_cos = glmer(responses_theme ~ theme_cosine_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "US", 
                               !(near(theme_frequency_E, .Machine$double.eps) & 
                                  near(tax_frequency_E, .Machine$double.eps))),

@@

```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE}
# Mandarin 
fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", 
                               !(near(theme_frequency_M, .Machine$double.eps) & 
                                  near(tax_frequency_M, .Machine$double.eps))), 
          family="binomial")
summary(fit.ZH_CN)
fit.ZH_CN.anova = Anova(fit.ZH_CN, type = 3)

fit.ZH_CN.anova

fit.ZH_CN_cos = glmer(responses_theme ~ theme_cosine_prop_M + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "China", 
                               !(near(theme_frequency_M, .Machine$double.eps) & 
                                  near(tax_frequency_M, .Machine$double.eps))),

          family="binomial")
summary(fit.ZH_CN_cos)
fit.ZH_CN_cos.anova = Anova(fit.ZH_CN_cos, type = 3)
fit.ZH_CN_cos.anova

fit.ZH_CN_compare_freq_cos = anova(fit.ZH_CN, fit.ZH_CN_cos, type = 3)
fit.ZH_CN_compare_freq_cos

```
# Does adding country help with the model (compared to with just English co-occurrence)? 
```{r}
fit.language = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(!(near(theme_frequency_E, .Machine$double.eps) & 
                                  near(tax_frequency_E, .Machine$double.eps))),

          family="binomial")
summary(fit.language)
fit.language.anova = Anova(fit.language, type = 3)
fit.language.anova

fit.country_language = glmer(responses_theme ~ theme_freq_prop_E * country + (1 | subject) + (1 | triad), 
          data = df %>% filter(!(near(theme_frequency_E, .Machine$double.eps) & 
                                  near(tax_frequency_E, .Machine$double.eps))),

          family="binomial")
summary(fit.country_language)

fit.country_language.anova = Anova(fit.country_language, type = 3)
fit.country_language.anova

fit.country_language_compare = anova(fit.language, fit.country_language, type = 3)
fit.country_language_compare
```

Adding country improves the model (thematic proportion of lexical co-occurrence, country, and their interaction were all significant predictors).

### 2022-12-14 code/3_analysis/3_paper_cogsci.Rmd
setting up cogsci paper

hi
```{r echo=TRUE, fig.align="center", fig.cap=c("List of triads used"), fig.show="hold"}
#include_graphics(c("../../data/SI_triads/SI_triads_1.jpg"))
include_graphics(c("../../data/SI_triads/SI_triads_1.jpg",
                   "../../data/SI_triads/SI_triads_2.jpg",
                   "../../data/SI_triads/SI_triads_3.jpg",
                   "../../data/SI_triads/SI_triads_4.jpg",
                   "../../data/SI_triads/SI_triads_5.jpg"))
```

>>>>

```{r echo=TRUE, fig.align="center", fig.cap=c("List of triads used"), fig.show="hold"}
#include_graphics(c("../../data/SI_triads/SI_triads_1.jpg"))
include_graphics(c("../../data/SI_triads/SI_triads_1.jpg",
                   "../../data/SI_triads/SI_triads_2.jpg",
                   "../../data/SI_triads/SI_triads_3.jpg",
                   "../../data/SI_triads/SI_triads_4.jpg",
                   "../../data/SI_triads/SI_triads_5.jpg"))
```
